\section{Core}

As its name suggests, the core is the central point of the PPP. It is
connected to all other components — user interfaces and modules — through
the protocol defined above, and is developed in Python\footnote{\url{https://github.com/ProjetPP/PPP-Core/}}.

The core communicates with the user interfaces and the modules {\em via} HTTP:
each time the core receives a request from an interface, it forwards it
to modules, using a configurable list of URL where to reach modules.

An example configuration is the one we use on the production server
(truncated):

\begin{verbatim}
{
    "debug": false,
    "modules": [
        {
            "name": "questionparsing_grammatical",
            "url": "python:ppp_questionparsing_grammatical.requesthandler:RequestHandler",
            "coefficient": 1,
            "filters": {
                "whitelist": ["sentence"]
            }
        },
        {
            "name": "cas",
            "url": "http://localhost:9003/cas/",
            "coefficient": 1,
            "filters": {
                "whitelist": ["sentence"]
            }
        },
        {
            "name": "spell_checker",
            "url": "python:ppp_spell_checker.requesthandler:RequestHandler",
            "coefficient": 1,
            "filters": {
                "whitelist": ["sentence"]
            }
        },
        {
            "name": "wikidata",
            "url": "http://wikidata.backend.askplatyp.us/",
            "coefficient": 1,
        },
        {
            "name": "datamodel_notation_parser",
            "url": "python:ppp_datamodel_notation_parser.requesthandler:RequestHandler",
            "coefficient": 1,
            "filters": {
                "whitelist": ["sentence"]
            }
        }
    ],
    "recursion": {
        "max_passes": 6
    }
}
\end{verbatim}

This example presents all the features of the core.

\subsection{Communicating with modules}

\begin{verbatim}
{
    "name": "cas",
    "url": "http://localhost:9003/cas/",
    "coefficient": 1,
    "filters": {
        "whitelist": ["sentence"]
    }
}
\end{verbatim}

This is the entry to connect the core to the CAS (Computer Algebra System)
module; that's the one which does the math. We provide a nice name (to be
shown in logs), the URL to know how to reach it, a coefficient applied to
the measures (see the chapter above, about the datamodel), and filters
(see above).

\subsection{Recursion}

\begin{verbatim}
    "recursion": {
        "max_passes": 6
    }
\end{verbatim}

This is why the core is more than just a router. Not only does it forward
requests to modules, and forward their answers to the client, but it can
make several passes on a request.

Let's take an example: the question “What is the caiptal of India?”.
\footnote{\url{http://askplatyp.us/?lang=en&q=What+is+the+caiptal+of+India\%3F}}
We need three passes to answer such a question.

\begin{enumerate}
    \item Spell-checking, to change it to “What is the capital of India?”
    \item Question parsing, to change it to a machine-understable query:
        “(India,capital,?)”
    \item Database request to Wikidata, to get the final answer:
        “New Delhi”
\end{enumerate}

After each pass, the router accumulates the different answers, until
there is no new answer. Then, it stops recursing and returns everything
to the client.
We also define a maximum to the number of passes; but it is not necessary
for now since modules we implemented cannot loop.

\subsection{Optimizations}

We implemented two optimizations in the core, that makes it faster (it is hard
to evaluate it; probably around 25\% less time on queries with multiple
passes).

The two of them are used in this example:

\begin{verbatim}
{
    "name": "questionparsing_grammatical",
    "url": "python:ppp_questionparsing_grammatical.requesthandler:RequestHandler",
    "coefficient": 1,
    "filters": {
        "whitelist": ["sentence"]
    }
}
\end{verbatim}

First, the filters (we talked about in the previous section). They can be
either a whitelist or a blacklist of root node types, that the core will
read in order to know if the module might do anything with such a tree.
Obviously, the question parsing modules cannot do anything with something
that is not a sentence, so it is useless to query them with something that
is not a sentence.

Secondly, the “python:” URL. The core can call directly Python modules
without using HTTP; and thus avoids the cost of serializing, using IPCs
(Inter-Process Communications), and deserializing (twice).
However, we need to run the module in the same process as the core in
order for this to work, so we only use it for light modules
(questionparsing\_grammatical and the spell-checker).

\section{Libraries for modules}

We also provide a library in charge of handling and parsing HTTP
requests following the format defined in the data model. It was originally
used in the core, but we then splitted the code, as modules can reuse
it without a change.
This class is an abstraction over a Python HTTP library (python-requests),
allowing module developpers to focus on developping their actual code
instead of handling communication.

These has proven to be efficient for connecting the Grammatical Question Parsing
with the Core: we only had to copy-paste the demo code
(used for reading and printing in the console) into a function called
by this library, and it was working as is.

It also exports its configuration library too, since modules share the
same way of handling configuration (a JSON file, whose path
is given {\em via} an environment variable).

For instance, here is the configuration file of the CAS module (Computer Algebra
System), used to allow system administrators to set memory and time limits
to computation:

\begin{verbatim}
{
    "max_heap": 10000000,
    "timeout": 10
}
\end{verbatim}
