\section{Overview}

Our search engine, \emph{Platypus}, is able to answer correctly to a wide range
of questions.

Here is a non-exhaustive list of questions with correct answer.

\subsection{Keyword questions}

\begin{itemize}
    \item Definition question.
    \begin{verbatim}
    Sherlock Holmes
    \end{verbatim}

    \item Depth-1 question.
    \begin{verbatim}
    author Les Misérables
    \end{verbatim}
\end{itemize}

\subsection{English questions}

\begin{itemize}
    \item Definition question.
    \begin{verbatim}
    What is “P=NP”?
    \end{verbatim}

    \item Location question.
    \begin{verbatim}
    Where is the capital of New Zealand?
    \end{verbatim}

    \item Depth-1 question, with quotation marks.
    \begin{verbatim}
    Who is the author of “Le Petit Prince”?
    \end{verbatim}
\end{itemize}

\subsection{Math questions}

\begin{itemize}
    \item Approximation of $\pi$ to the $42^{th}$ digit.
    \begin{verbatim}
    N[Pi, 42]
    \end{verbatim}

    \item Exact value of $\lim_{n\rightarrow \infty} \sum_{i=1}^n \frac{1}{i} - \log(n)$.
    \begin{verbatim}
    Limit[Sum[1/i, {i,1,n}]-Log[n], n->Infinity]
    \end{verbatim}
\end{itemize}

\subsection{Weird questions}

\begin{itemize}
    \item Spelling mistake.
    \begin{verbatim}
    What is the cappyttal of Franse?
    \end{verbatim}

    \item Nested question.
    \begin{verbatim}
    Who are the daughters of the wife of the husband of the wife of the president
    of the United States?
    \end{verbatim}
\end{itemize}

\section{Comparison with existing tools}

We study the ability of our tool to successfully answer to questions, in comparison
to \emph{WolframAlpha}\footnote{\url{https://www.wolframalpha.com/}}, one of the best
question answering engine.

\subsection{Nested questions}

A nested question is a question with several level of knowledge. For instance, the
question "What is the birth date of the first person to walk on the moon?" requires
firstly to know that Neil \textsc{Armstrong} was the first person to walk on the
moon and then to know that he was born on August 5, 1930.

Our search engine tends to be more successful than \emph{WolframAlpha}
on such questions. We explain this by the fact that nested questions are generally
well structured and therefore good candidates for a grammatical analysis.

Some examples:

\begin{tabular}{l|l}
    \multicolumn{2}{l}{Who is the mayor of the capital of Czech Republic?} \\
    \hline
    \textbf{WolframAlpha} & Prague\\
    \textbf{Platypus} & Tomáš Hudeček\\
\end{tabular}

\begin{tabular}{l|l}
    \multicolumn{2}{l}{When was born the author of "Sherlock Holmes"?} \\
    \hline
    \textbf{WolframAlpha} & no result\\
    \textbf{Platypus} & Sunday, May 22, 1859\\
\end{tabular}

\begin{tabular}{l|l}
    \multicolumn{2}{l}{What is the citizenship of the daughters of the wife of the president of the United States?} \\
    \hline
    \textbf{WolframAlpha} & Barack Obama\\
    \textbf{Platypus} & United States of America\\
\end{tabular}

\subsection{Conjunction questions}

A conjunction is a question which require to do either an union of sets or an intersection
of sets. For instance, the question "Who has been a Jedi and a Sith?" requires to
compute the intersection of the members of the Jedi organization and the Sith organization,
to find out all the persons that has been in both organizations.

Thank to the union and the intersection of our data model, our search engine also
provide better answers for such questions.

An example:

\begin{tabular}{l|l}
    \multicolumn{2}{l}{Who is the actress of "Pulp Fiction" and "Kill Bill"?} \\
    \hline
    \textbf{WolframAlpha} & the whole casting of this two films\\
    \textbf{Platypus} & Uma Thurman\\
\end{tabular}


\section{Limitations}

Platypus is still limited to the knowledge of \emph{Wikidata} and to some grammatical
structures.

\emph{Wikidata} does not contain any information about measures. We are unable
to answer to questions like "How far is the Sun?", "How small is an atom?" or
"What is the speed of Ariane 5?".

We are also unable to parse correctly sentences with a more complex structure, like
"From which country does the jazz come from?".
